Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
2.3

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}
\usepackage{xspace}

@@

\subsection{Message-oriented Dependencies}
Given deadlines and partial reliability, the next important transport
service is \emph{dependency management}. There is no point in sending data
that cannot be used because it depends on previous data that was not
received. Providing this service is complicated by the two ways in which
data can be \emph{useful} to applications: it may itself by played out, or
it may be needed as part of the application's decoding chain. For example,
an I frame provides utility both in being played out, and in allowing for
subsequent P and B frames. As a result, dependency information may result
in deadline information being overruled: data may be sent even if it cannot
be played out, if it is necessary for the decoding of other data.

Providing partial reliability, through deadlines and dependencies, requires
the use of application-level framing \cite{clark:1990:architecture} to
make the best use of payload data, irrespective of packet loss. At the
transport layer, this implies that we provide a \emph{message oriented}
service, that maintains ADU boundaries.

Many multimedia applications make use of multiple data flows. For example,
a simple IPTV application will maintain separate audio and video flows.
These could be sent across multiple transport-layer connections, but
overheads can be reduced by multiplexing these flows on a single
connection. A \emph{sub-stream} service allows this.

@@

The architecture of TCP Hollywood is shown in Figure
\ref{diagram:tcp-hollywood}. TCP Hollywood implements all of the services
described in Section \ref{sec:services}, splitting functionality across
an intermediary layer in user-space, and a set of modifications to the
kernel. This split allows applications to program against one API, whether
or not the kernel modifications are available: the intermediary layer
functions in both cases.

At the sender, applications pass messages (using an API similar to that
given in Table \ref{tab:api}) to the intermediary layer, with their
metadata, including deadline and dependency information. At the 
intermediary layer, COBS encoding \cite{CB97COBS} is used to escape all
zero bytes in the message data, allowing them to be used as framing
markers. The message's metadata is then attached to the encoded and framed
message, before being passed to the kernel using the standard Berkeley
sockets API.

At the kernel, the message data is queued in TCP's sending buffer, while
the metadata is held in a separate structure. Nagle's algorithm, designed
to coalesce smaller writes into larger segments, is disabled to minimise
latency. As segments are (re-)transmitted, their deadlines and dependencies
are checked to ensure that the message will be useful on arrival. In the
current version of TCP Hollywood, the dependency check does not overrule
the deadline check: only data that can be played out will be sent. If the
message does not pass the liveness check, the next message in the queue
that is live will be sent instead. If this is a retransmission, then
inconsistent retransmissions will be used: the replacement message will be
sent with the same TCP sequence number as the original.

At the receiver, segments are passed to the kernel, where they are
initially processed as under standard TCP: duplicate acknowledgements are
generated for out-of-order segments, for example. After this, a metadata
entry is created, and placed in FIFO queue. When the intermediary layer
reads from the socket, it receives the segment associated with the
metadata entry at the head of the queue, with its TCP sequence number
attached.

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. Any message fragments are buffered,
alongside their TCP sequence number, awaiting the arrival of the remainder
of the message. Once the message has been reassembled, it is decoded, and
delivered to the application.

TCP Hollywood inherits standard TCP's congestion control mechanism.
Clearly, being a loss-based algorithm, this is not appropriate for
real-time applications.
\todo{discuss how we need to change TCP congestion control}

>>>>

\documentclass[10pt]{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}
\usepackage{xspace}

@@

\subsection{Message-oriented Dependencies}

The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: It may itself
by played out, or it may be needed as part of the application's decoding chain.
For example, I frames provide utility both in being played out, and as
foundations for subsequent P and B frames. As a result, dependencies may take
higher priority than deadlines.
% : data may be sent even if it
% cannot be played out, if it is necessary for the decoding of other data.

Partial reliability in the context of both deadlines and dependencies
requires application-level framing \cite{clark:1990:architecture} to
make the best use of payload data, irrespective of packet loss. At the transport
layer, this implies that we provide a \emph{message oriented} service, that
maintains ADU \todo{first mention?} boundaries.

Message orientation may also be used to construct a \emph{sub-stream} service.
Many multimedia applications make use of multiple data streams. For example, a
simple IPTV application will maintain separate audio and video stream. These
could be sent across multiple transport-layer connections, but overheads can be
reduced by multiplexing these flows on a single connection.

@@

The architecture of TCP Hollywood is shown in
Figure \ref{diagram:tcp-hollywood}. TCP Hollywood provides all of the
services described in Section \ref{sec:services}, with functionality split
across an intermediary layer (in user-space), and a set of modifications to
the kernel. The intermediary layer is responsible for providing the
message-oriented abstraction, and exposing the API for partial reliability.
The kernel modifications implement the deadline and dependency services,
as well as enabling out-of-order delivery of incoming segments. This split
allows applications to use a single API, whether or not the kernel
modifications are available. TCP Hollywood inherits standard TCP's
congestion control mechanism. Clearly, this loss-based mechanism is not
suitable for real-time applications, and a delay-based algorithm should
be adopted.

\todo{Stephen: give more detail, and expand this to a whole column}

\todo{discuss how we need to change TCP congestion control}
